# Introduction {#intro}

```{r}
library(dplyr)
library(kableExtra)
```

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

This is the reference part of equation \@ref(eq:random).

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

```{r class.source = "watch-out", include=TRUE}
Comp <- c("B","G","BB","BG","GB","GGB","GBB","Total")
Likcomp1 <- c("$p_B$",
              "($1-p_B$)",
              "$p^2_B$",
              "$p_B(1-p_B)$",
              "$(1-p_B)p_B$",
              "$(1-p_B)^2 p_B$",
              "$\\displaystyle\\frac{(1- \\lambda^R)\\beta^2_B}{2 \\gamma}$",
              " ")
Numfamis <- c(6,7,5,4,5,1,2,30)
Likcomp2 <- c("$p^6_B$",
              "$(1-p_B)^7$",
              "$p^{10}_B$",
              "$p^4_B(1-p_B)^4$",
              "$(1-p_B)^5 p^5_B$",
              "$(1-p_B)^2 p_B$",
              "$(1-p_B)^2 p^4_B \\geq \\gamma$",
              " ")
```

```{r table2chp2, echo=FALSE}
#lik50.tab
table2chp2 <- data.frame(Comp, Likcomp1, Numfamis, Likcomp2)
kable(table2chp2, booktabs = T,
      col.names = c("Composition",
        "Likelihood contribution for one family",
        "Number of families",
        "Likelihood contribution for multiple families"),
      caption = "The likelihood factors for the hypothetical data set of n=50 children.", 
      escape=F) %>%
  column_spec(c(2,4), width = "4cm") %>% 
  kable_styling(latex_options = "scale_down")
```

\begin{align}
 \hat{p}_{B|\textrm{B Bias}}&= \frac{1131}{1131+1164}\\
 & =  0.4928 \\
 &  \\
 \hat{p}_{B|\textrm{G Bias}}&=\frac{1124}{1124+973}\\
&= 0.5360
(\#eq:random)
\end{align}

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
